Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2022-06-16 analysis/paper_draft2.Rmd
Update paper_draft2.Rmd
added text about compatibility plot

In practice, the anticipated degree of incompatibility should influence which value of $\alpha$ to select. For example, given perfect compatibility ($\mid b_{curr} - b_{hist} \mid = 0$), then we should let $\alpha = 1$ (equal weight between current and historical data). This will maximize the model's ability to detect bias, even when the number of strikes is small. This effect of increased bias detection can be seen in the simulation plots above, along the positive diagonals of the individual blocks, and is strengthened by increasing the number of historical trials and number of strikes.

>>>>

In practice, the anticipated degree of incompatibility should influence which value of $\alpha$ to select. For example, given perfect compatibility ($\mid b_{curr} - b_{hist} \mid = 0$), then we should let $\alpha = 1$ (equal weight between current and historical data). This will maximize the model's ability to detect bias, even when the number of strikes is small. This effect of increased bias detection can be seen in the simulation plots above, along the positive diagonals of the individual blocks, and is strengthened by increasing the number of historical trials and number of strikes. Higher bias detection rates are obtained for higher values of alpha, acorss compatibility scenarios (Fig X). This effect is most pronounced for scenarios with a low number of strikes and few historical trails (top left paned of fig X).  There is less of an effect of $\alpha$ on the bias detection rate when bias is high, the number of strikes is high, and the number of historical trials is high  (lower right panel of fig X). Overall, though, increasing $\alpha$ will increase bias detection under current and histrotical trial compatiblity.
